An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-06-02 poly-embed-journal/poly-embed-journal.tex
Pass over Sec 3

\subsection{Links and Embeddings}
\label{sec:links-embeddings}

@@

Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
We formalize this notion as follows.

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set}\jessiet{Propogate change} if it has the smallest cardinality among all representative sets.
\end{definition}
Minimum representative sets are essentially the same as \emph{maximally informative sets} from~\citet{wang2020weston}, but we found the name minimum representative set to give more intuition about being the smallest such set.

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ and $L:\reals^d\to\reals^\Y$

@@

\begin{proposition}\label{prop:SL-minimal}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.

	To show that $L$ has a polyhedral Bayes risk implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
	Each facet $F$ of the epigraph of negative risk $E_L$ must be full dimensional by definition of a facet.
	Take $p \in \inter{F}$, and observe that it must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$.
	Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
	We show $\Sc$ is a minimum representative set (it is finite as $L$ polyhedral implies it has finitely many facts, so $\Sc$ is generated over a finite set.)

	First, we have to show that $\Sc$ is a representative set.
	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ (epigraph of negative risk) exactly on facet (and therefore $u_F \in \Gamma(p) \cap \Sc(L)$ for all $p$ such that the hyperplane supports $E_L$ at $p$), we have $\Sc(L)$ representative for $L$.
	Representativeness follows the facets of $E_L$ union to the simplex.

	If $\Sc$ was not a minimum set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
	By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
	There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
	We particularly have $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
	By construction of $\Sc$, we must have only added at most one of these to the set.
	Therefore, $\Sc$ is a minimum representative set.

@@

	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
	Construct $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimal}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
	Such an embedding is well-defined as the facets are the same since the risks are equal.
	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.  For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.  Form $\Sc$ from the set of such reports $r$, iterating over each facet.  We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed. Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.

We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
To verify matching losses, consider that the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(\varphi(r))})$ are exactly equal since they are linear functions matching on a set of positive measure relative to the simplex, and must be equal everywhere.
This implies $\ell(r) = L(\varphi(r))$ for all $r \in \Sc$ such that the hyperplanes support $E_\ell$ and $E_L$ on a facet.
Since $\Sc$ and $\U$ are minimum representative sets, this holds for all $r \in \Sc$.
%To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
%\jessie{This feels like it's missing a detail about how $\Sc$ is minimal and how level sets are full-dimensional.}
\end{proof}

@@

In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimal}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

This allows us to reason about the range of the property elicited by a polyhedral loss; in particular, it is finite.
See \S~\ref{app:power-diagrams} for the full proof.

\begin{restatable}{lemma}{polyhedralrangegamma}
	\label{lem:polyhedral-range-gamma}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix}
\end{restatable}
\begin{proof}[Sketch]
	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
	Moreover, we have $\Gamma(p)$ being exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value.
	Since this epigraph has finitely many faces, the range of $\Gamma$ is then (a subset) of elements of a finitely generated (finite supports) set of finite elements (finite faces).
\end{proof}

@@

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  we use the same technique as in the proof of Proposition~\ref{prop:embed-bayes-risks}.
Consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that reduces to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}

@@

% commented out 19 Apr 21
% \raf{Some thoughts on this section:
% \begin{itemize}
% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%   \begin{itemize}
%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%   \end{itemize}
% \end{itemize}}
% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
% There are a few results that are well-explained by this:
% \begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimally representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
% \end{itemize}
% This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

@@

@@

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $R^*$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimal representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.

@@

%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

@@

%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimal. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

@@

% \paragraph{Directions.}
%\jessie{Getting rid of this given the COLT-20 paper}
%\iffalse
%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimal dimension}?
%If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
%As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
%\fi

@@

Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.

>>>>

\subsection{Calibration and consistency \jessie{Change}}
\label{sec:links-embeddings}

@@

\subsection{Embeddings}
Several consistent convex surrogates in the literature can be thought of as ``embeddings'', wherein one maps the discrete reports to a vector space, and finds a convex loss which agrees with the original loss.
A key condition is that the original reports should be optimal exactly when the corresponding embedded points are optimal.
We formalize this notion as follows.

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set} if it has the smallest cardinality among all representative sets.
\end{definition}
Minimum representative sets are essentially the same as \emph{maximally informative sets} from~\citet{wang2020weston}, but we found the name minimum representative set to give more intuition about being the smallest such set.

@@

In this section, we establish a tight relationship between the technique of embedding and the use of polyhedral (piecewise-linear convex) surrogate losses.
We defer the question of when such surrogates are consistent to \S~\ref{sec:calibration}. 
Throughout this section, unless specified otherwise, we use $\ell:\R\to\reals^\Y$ for discrete target losses and $L:\reals^d\to\reals^\Y$ for surrogates.

@@

\begin{proposition}\label{prop:SL-minimum}
  A loss $L: \R \to \reals^\Y_+$ has a polyhedral Bayes risk if and only if it has a finite minimum representive set.
  Moreover, for any minimum representative set $\Sc$ for $L$, there is a bijection between $\Sc$ and the facets of the epigraph of $-\risk{L}$.
  \raft{Jessie: prove :-].  Note: min rep $\implies$ poly risk is immediate from Lemma~\ref{lem:loss-restrict}.  Move the construction into the proof. \jessie{Done; ready for a look}}
\end{proposition}
\begin{proof}
	Finite minimum representative implies polyhedral Bayes risk as a corollary of Lemma~\ref{lem:loss-restrict}.

	To show that $L$ has a polyhedral Bayes risk implies it has a finite minimum representative set, we construct the set $\Sc$ as follows:
	since the epigraph of negative Bayes risk $E_L$ is polyhedral, it has finitely many facets, and we iterate over these.
	Each facet $F$ of $E_L$ must be full dimensional by definition of a facet, and therefore there must be some $p \in \inter{F}$.
	Observe that $p$ must by uniquely supported by some hyperplane $p \mapsto (p, L(u))$ for some $u \in \R$, since it is in the interior of the facet (and therefore $\risk{L}$ is differentiable at $p$).
	Add $u$ to $\Sc$, and repeat, iterating over each of $E_L$'s finitely many facets.
	We now show $\Sc$ is a minimum representative set.

	First, we have to show that $\Sc$ is a representative set.
	As facets are closed, for each facet $F$ and $p_F \in F$, there is a report $u_F \in \Sc$ by construction and closedness of facets so that the hyperplane $p_F \mapsto (p_F, \inprod{p_F}{L(u_F)})$ supports $E_L$ exactly on the facet. Therefore $u_F \in \Gamma(p) \cap \Sc$ for all $p$ such that the hyperplane supports $E_L$ at $p$.
	Representativeness follows as the facets of $E_L$ union to the simplex.

	If $\Sc$ was not a \emph{minimum} representative set, then we could remove some $s$ from $\Sc$ such that $\Sc' := \Sc \setminus \{s\}$ is also a representative set for $L$.
	By the construction of $\Sc$ over facets of $E_L$, this report $s$ corresponds to a facet $F$ of $E_L$ since facets are full-dimensional and thus have well-defined nonempty interiors.
	There is then some distribution $p_F \in \inter F$ such that the hyperplane $p \mapsto (p, L(s))$ uniquely supports $E_L$ at $p_F$.
	We claim $\Gamma(p) \cap \Sc' = \emptyset$, since any other element $s'$ of $\Sc'$ being in $\Gamma(p)$ would imply $p \mapsto (p, L(s'))$ also supports $E_L$, but this hyperplane supporting $E_L$ must be unique, so these are equal.
	By construction of $\Sc$, we must have only added at most one of these to the set.
	Therefore, $\Sc$ is a minimum representative set.

@@

	\jessiet{Not sure how much this matters, but technically, the $\Sc$ here might be different from the $\Sc$ in the forward implication, and might even be different cardinalities. Not sure if we want to change the notation to reflect this, or if that would just add confusion.}
	For the reverse implication, assume $\risk{L} = \risk{\ell}$, which are polyhedral functions as $\ell$ is discrete.  
	Construct a minimum representative set $\Sc$ via a bijection from the facets of $E_\ell$ as in the proof of Proposition~\ref{prop:SL-minimum}, and $\U$ similarly from $E_L$, with the embedding $\varphi : r \mapsto u_r$ if the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(u_r)})$ are equal.
	Such an embedding is well-defined as it is the composition of the bijections from reports in $\Sc$ and $\U$ to facets.
	%Since $\risk{\ell}$ is polyhedral, the epigraph of its negation, $E_\ell$, has a finite set of facets, which by definition have well-defined interiors.  For each facet, there must then be some distribution $p_r$ and report $r \in \R$ such that the hyperplane $p_r \mapsto (p_r, \inprod{p_r}{-\ell(r)})$ uniquely supports $E_\ell$.  Form $\Sc$ from the set of such reports $r$, iterating over each facet.  We have $\Sc$ representative for $\ell$ since the union of projected epigraph facets equals the simplex, and these facets and their projections are closed. Therefore, every $p \in \simplex$ is contained in some facet of the epigraph, and thus there is some $r \in \Sc$ so that $r \in \gamma(p)$.
%As the risks are equal, the same is true for $E_L$, e.g., for each facet, there is some $u_r$ so that $p_r \mapsto (p_r, \inprod{p_r}{L(u_r)})$, and one can construct the embedding $\varphi: r \mapsto u_r$ for each $r \in \Sc$.

We match optimality of embedded reports by construction, since the optimal reports support the epigraph of negative Bayes risk on exactly the same distributions, meaning a report and its embedding are optimal at exactly the same distributions.
To verify matching losses, consider that the hyperplanes $p \mapsto (p, \inprod{p}{\ell(r)})$ and $p \mapsto (p, \inprod{p}{L(\varphi(r))})$ are exactly equal since they are linear functions matching on a set of positive measure relative to the simplex, and must be equal everywhere.
This implies $\ell(r) = L(\varphi(r))$ for all $r \in \Sc$ such that the hyperplanes support $E_\ell$ and $E_L$ on a facet.
Since $\Sc$ and $\U$ are minimum representative sets, this holds for all $r \in \Sc$.
%To verify matching losses, observe $\risk \ell (\delta_y) = \risk L (\delta_y)$ for each $y \in \Y$, and these risks are attained by some report $r$ and its embedding $u_r$, respectively.
%\jessie{This feels like it's missing a detail about how $\Sc$ is minimum and how level sets are full-dimensional.}
\end{proof}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  Form the finite set $\Sc$ as the proof of Proposition~\ref{prop:SL-minimum}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

Shifting our focus to \emph{polyhedral} (piecewise linear and convex) surrogates, we observe that these surrogates elicit finite properties, though they may have optimal sets that are infinite.
This lets us apply results about finite representative sets to understand the structure of polyhedral surrogates and the losses they embed.
See \S~\ref{app:power-diagrams} for the full proof.

\begin{restatable}{lemma}{polyhedralrangegamma}
	\label{lem:polyhedral-range-gamma}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
	Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d : p\in\simplex\}$, is a finite set of closed polyhedra.
        \raft{Leave this statement and add a proof sketch; move other dependencies to appendix \jessie{Done feel free to burn}}
\end{restatable}
\begin{proof}[Sketch]
	With $\Y$ finite, there are only finitely many supporting sets over $\simplex$.
	For $p \in \simplex$, the power diagram induced by projecting the epigraph of expected loss onto $\reals^d$ is the same for any $p$ of the same support (Lemma~\ref{lem:polyhedral-pd-same}).
	Moreover, we have $\Gamma(p)$ being exactly one of the faces of the projected epigraph since the hyperplane $u \mapsto (u, \inprod{p}{L(u)})$ supports the epigraph of the expected loss at exactly the property value.
	Since this epigraph has finitely many faces, the range of $\Gamma$ is then (a subset) of elements of a finitely generated (finite supports) set of finite elements (finite faces).
\end{proof}

@@

\proposedadd{Moreover, to construct an embedding of dimension $n-1$ instead of $n$ (see~\citet{finocchiaro2020embedding} for significance of dimension),  consider some invertible linear transformation $A : \reals^n \to \reals^{n-1}$ that maps to an affine subspace.
Take $L' : \reals^{n-1} \to \reals^\Y$ as $x \mapsto L(A^{-1}(x))$ and $L$ defined as above, so that $\inprod{\ell(r)}{p} = \inprod{L(\varphi(r))}{p} = \inprod{L'(A^{-1}(\varphi(r)))}{p} $ for all $p \in \simplex$.
The Bayes risks $\risk{L}(p)$ and $\risk{L'}(p)$ are equal for all $p \in \simplex$; thus, the result holds in $n-1$ dimensions as well.}\jessiet{Leaving this change in the macro for proofreading.}

@@

% commented out 19 Apr 21
% \raf{Some thoughts on this section:
% \begin{itemize}
% \item It's unclear to me how much of the properties stuff is for funzies versus useful in the sense that it's clearer to dispense with the loss.
% \item It seems nice to point out and explore the fact that our notion of embedding is, now, symmetric.
%   \begin{itemize}
%   \item So generally we could say $L_1:\R_1\to\reals^\Y$ and $L_2:\R_2\to\reals^\Y$ are \emph{equivalent} (name TBD) if there exist $\Sc_i\subseteq\R_i$ representative for $L_i$, $i\in\{1,2\}$, with a bijection $\varphi:\Sc_1\to\Sc_2$ such that (i) for all $r\in\Sc_1$ we have $L_2(\varphi(r)) = L_1(r)$, and (ii) for all $p\in\simplex, r\in\R_1$ we have $r\in\prop{L_1}(p) \iff \varphi(r)\in\prop{L_2}(p)$.
%   \item Now since $\varphi$ is a bijection it's clear that this is an equivalence relation.
%   \item Moreover, since we've already established (Prop~\ref{prop:embed-bayes-risks}) that if $L$ embeds discrete $\ell$ over $\Sc$, then $\Sc$ being representative for $\ell$ implies $\varphi(\Sc)$ is representative for $L$, meaning $L$ and $\ell$ are equivalent under this definition.
%   \item What other results might hold more generally using this equivalence notion?  (Note: finiteness of $\Sc$ is not assumed now, though we could make that assumption.)
%   \item I believe the Bayes risk matching result may hold: $L_1$ and $L_2$ are equivalent iff $\risk{L_1}=\risk{L_2}$.  Certainly the first direction (equivalent $\implies$ risk matching) goes through untouched.  For the converse, I think we need finiteness of $\trim$, or maybe more generally some condition about the differentiability of the risk, since we needed the uniqueness of the supporting hyperplane to $\risk{L}$ to deduce that the losses matched.  Otherwise, if the Bayes risk has a nondifferentiable point, and the the level set of $u$ is that point, and $u$ is not redundant, there will be multiple loss vectors at $u$ which achieve the same Bayes risk.
%   \end{itemize}
% \end{itemize}}
% \jessie{Thinking about this: I think there is enough value to $\trim$ as an object to include it.  The concept makes a lot more intuitive sense if we defined it by $\trim_\Sc(\gamma) = \{\gamma_r : r \in \Sc\}$ and thinking about the importance of $\Sc$.
% There are a few results that are well-explained by this:
% \begin{itemize}
%	\item $L$ embeds discrete $\ell$ over set $\Sc$ (minimum representative for $\ell$) iff $\trim_\Sc(\prop{\ell}) = \trim_{\varphi(\Sc)}(\prop{L})$
%	\item $L$ is equivalent to discrete $\ell$ iff $\trim_{\R_1}(\prop{\ell}) = \trim_{\R_2}(\prop{L})$
%	\item when is $\ell$ non-redundant? (no reports $r$ s.t. $\gamma_r$ is (a) empty, (b) not a strict subset of another level set, or (c) exactly equal to another level set.)
%	\item can't have reports that are strict subsets and on a facet of the epigraph <-- less clear how this would follow in this section.
% \end{itemize}
% This begs the question: what is the utility of non-redundancy?  It feels like getting rid of redundant reports makes it easier to study the property, where they don't really hurt much when studying the loss.}

@@

In \S~\ref{sec:poly-loss-embed}, we discuss some implications of a representative set being minimum; here, we further investigate the relationship between minimum representative sets, non-redundancy of losses, and introduce what it means for an embedding to be tight.

@@

\begin{corollary}\label{prop:trim-loss-condition}
  Given an loss $L : \R \to \reals^\Y_+$ with finite minimum representative set $R^*$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{corollary}
\begin{proof}[Sketch]
  Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
  The only time $\U$ contains redundant elements is if there is $u,u' \in \U$ so that $\Gamma_u = \Gamma_{u'}$.  In such a case, removing duplicate elements of $\U$ to form $\U^*$ means $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U^*\}$ and $L|_{U'}\}$ is nonredundant, and therefore $\U^*$ is a minimum representative set by Proposition~\ref{prop:tfae-min-rep-nonredundant}, and therefore equal to $\trim(L)$.

@@

%  If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\U'$ is minimum. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

@@

%  % If there was a level set $\Gamma_u$ for some $u \in \varphi(\R')$ that was not full-dimensional, it would have to be a subset of some other level set $\Gamma_{u'}$, but this contradicts that $\varphi(\R')$ is minimum. \jessie{Hand waving; make the argument you can't span relints of other level sets.}

@@

% \paragraph{Directions.}
%\jessie{Getting rid of this given the COLT-20 paper}
%\iffalse
%One open question of particular interest involves the dimension of the surrogate prediction space; given a discrete loss, can we construct a surrogate that embeds it \emph{of minimum dimension}?
%If we na\"ively embed the reports into an $n$-dimensional space, the dimensionality of the problem scales linearly in the number of possible labels $n$.
%As the dimension of the optimization problem is a function of this \emph{embedding dimension} $d$, a promising direction is to leverage tools from elicitation complexity~\cite{lambert2008eliciting,frongillo2015elicitation} and convex calibration dimension~\cite{ramaswamy2016convex} to understand when we can take $d <\!\!< n$.
%\fi

@@

Proposition~\ref{prop:embed-bayes-risks}, focuses on matching the values of Bayes Risks, while the following result from~\citet{aurenhammer1987power} allows us to move towards understanding the projection of the Bayes Risk onto the simplex $\simplex$.
In particular, one can consider the epigraph of a polyhedral convex function on $\reals^d$ and the projection down to $\reals^d$; in this case we call the resulting power diagram \emph{induced} by the convex function.
